Notes on area-length problem for CLE

### 2013-08-12 area-length/notes.tex
Some text
Sections and abstract are added

\begin{abstract}
  Here I document staff related to my work on area-length problem.
\end{abstract}

>>>>

\begin{abstract}
  Here I document staff related to my work on area-length problem.

  We consider the scaling limit of conformal loop ensemble. The ratio
  of loop area to certain power of loop length exhibit universal
  scaling behavior. Scaling function is proportional to Bessel's
  function. We show it using fusion rules for degenerate field in
  conformal field theory on a cone. 
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Here we discuss the history of the problem and state our answer to it.

\section{Scaling of random loops}
\label{sec:scaling-random-loops}

In this section we introduce scaling function for random loops.

Consider rooted loops in $O(n)$ model. Let $N^r(L)$ be number of
rooted loops with a given length.  By $N^r(L,A)$ we denote the number
of loops of given length and area. $N^r(L)=\int_0^{\infty} N^r(L,A)
dA$. Area weighted number of loops is denoted by $G^r(L,\mu)$. (Here
$\mu$ is bulk coupling constant ?).
\begin{equation}
  \label{eq:2}
  G^r(L,\mu)=\int e^{\mu A} N^r(L,A) dA
\end{equation}

\begin{equation}
  \label{eq:1}
  G^r (\mu,x) = \sum_{\mathrm{clusters}} N^r (L,A) x^L e^{-\mu A}
\end{equation}

The idea is to write $G$ as a correlation function in Liouville
theory.

\section{Scaling limit and CFT on a cone}
\label{sec:scaling-limit-cft}

Here we argue that scaling limit is connected with correlation
functions of CFT on a cone. Then we introduce recurrence relations on
the angle of the cone. We show that this recurrent relation is
equivalent to fusion rules of degenerate field in CFT.

\section{CFT fusion coefficients and Bessel's functions}
\label{sec:cft-fusi-coeff}

In this section we solve recurrent relation using fusion rules and
show that scaling function is equal to Bessel's function.

\section{Conclusion}
\label{sec:conclusion}
Some concluding remarks are here.
